Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-09 msbr_reproc.tex
minor grammar fix

Recently, interest in \glspl{MSR} has resurged, with multiple new companies 
pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 
liquid-fueled molten salt designs from Transatomic, Terrapower, Terrestrial, 
and Thorcon.}.
To further develop these \gls{MSR} concepts, particularly with respect to their  
strategies for online reprocessing and refueling, advanced
computational analysis methods capturing
their unique reactor physics and process chemistry are needed.
Most contemporary nuclear reactor physics software is unable
to perform depletion calculations in an online reprocessing 
regime. Powers \emph{et al.} suggested a novel method to conducting 
depletion simulation for \gls{MSR} with taking into account the online 
reprocessing and refueling based on the deterministic computer code NEWT in 
SCALE \cite{powers_new_2013}. This approach was later used by Jeong \emph{et 
al.} to find an equilibrium fuel composition for \gls{MSBR} and to validate it 
with an \gls{MCNP}/CINDER90 
model \cite{jeong_equilibrium_2016}.

>>>>

Recently, interest in \glspl{MSR} has resurged, with multiple new companies 
pursuing commercialization of \gls{MSR} designs\footnote{Examples include both 
liquid-fueled molten salt designs from Transatomic, Terrapower, Terrestrial, 
and Thorcon.}.
To further develop these \gls{MSR} concepts, particularly with respect to their  
strategies for online reprocessing and refueling, computational analysis methods capturing
their unique reactor physics and process chemistry are needed.
However, most contemporary nuclear reactor physics software is unable to 
perform depletion calculations in an online reprocessing 
regime. Powers \emph{et al.} suggested a novel method for conducting 
depletion simulations for \gls{MSR}. This suggested method takes into account 
fuel salt composition changes due to online 
reprocessing and refueling based on the deterministic computer code NEWT in 
SCALE \cite{powers_new_2013}. This approach was later used by Jeong \emph{et 
al.} to find an equilibrium fuel composition for the \gls{MSBR} and was 
validated with an \gls{MCNP}/CINDER90 model \cite{jeong_equilibrium_2016}.
